\LARGE \bf ***

### 2020-09-24 icra-2021.tex
maybe the problem statement works?

Energy planning algorithms for mobile robots broadly are not a new concept and have been extensively studied, in that they are correlated to such topics as trajectory generation and path planning. Generally, these algorithms account for the energy due to the trajectory, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2004energy}. And computations are only expected to increase in future scenarios. For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Further, past mission planning approaches also limit to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, and to the class of robots~\cite{sadrpour2013mission,sadrpour2013experimental}. Unlike these approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands.

The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flyes and its batteries drain. The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes. It optimizes TEEs--an abstraction of the path to follow--and moves the UAV using a vector field that converges smoothly to the path. Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a commercial fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

@@

\begin{center}\vspace{.2cm}---\emph{this section is not good (needs work)}---\vspace{.6cm}\end{center}

Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with researchers fulfilling some of the demands applying mobile robots in agricultural scenarios such as harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}. In these scenarios, complex monitoring strategies, often implemented utilizing unmanned aerial vehicles (UAVs), are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.

%%%%%%%%%%%%%%%
\section{Model}
\label{sec:model}

The algorithm uses the model to estimate the UAV's position in space and its energy evolution in time.

Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t. some inertial navigation frame $\mathcal{O}_W$, we build a guidance action--which allows the motion along the 3-axis--to the path to follow using a vector field~\cite{de2017guidance}. The path is a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$ (the TEE is being satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points).

We build the energy evolution $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.

@@

We consider a non-holonomic 2D model of the fixed-wing UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ (the requirement is eased in Section~\ref{sec:algo} to a set of altitudes $\mathbf{h}$)
\begin{equation}\label{eq:uav-kinem}\begin{cases}
  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+\mathbf{d}(t)\\
  \dot{\psi}(t)&=u(\mathbf{p}(t))
\end{cases},
\end{equation}
where $\mathbf{p}\in\mathbb{R}^2$, $s\in\mathbb{R}$ is the airspeed (assumed constant), $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi)=\begin{bmatrix}\cos{\psi} & \sin{\psi}\end{bmatrix}^T$, $\mathbf{d}\in\mathbb{R}^2$ is the wind vector (assumed $\|\mathbf{d}\|<s$, i.e., the constant airspeed is greater than the norm of the wind), and $u\in\mathbb{R}$ the guidance action--the angular velocity $\dot{\psi}$ of the UAV.

@@

Let us define $\varPhi:=\varphi_k(\mathbf{p})$. The direction to follow can be expressed as the desired velocity vector
\begin{equation}\label{eq:pd}
  \dot{\mathbf{p}}_d(\mathbf{p}):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
    0&1\\-1&0
  \end{bmatrix},
\end{equation}
where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.

@@

The guidance action can be expressed
\begin{equation}\label{eq:uav-cont}
  u(\mathbf{p},\psi)=\frac{\|\dot{\mathbf{p}}\|}{s\cos{\gamma}}\left( \dot{\mathbf{\chi}}_d+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
\end{equation} 
where $k_d\in\mathbb{R}_{\geq 0}$ is the gain to adjusts the speed of convergence of $\dot{\mathbf{p}}_d$, $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, and $\dot{\chi}_d:=\dot{\chi}_d(\mathbf{p})$ is given in Equation~(\ref{eq:chid}).

>>>>

Energy planning algorithms for mobile robots broadly are not a new concept and have been extensively studied, in that they are correlated to such topics as trajectory generation and path planning. Generally, these algorithms account for the energy due to the trajectory, by e.g., maximizing the operational time~\cite{wahab2015energy}, but in practice apply to a narrow class of robots~\cite{kim2005energy}, and focus on optimizing motion control for such robots~\cite{kim2008minimum}, despite compelling evidence for these systems' energy being influenced by the computations over bare motion~\cite{mei2004energy}. For UAVs specifically, rotorcrafts have equally gained research interest in terms of algorithms for energy-efficient trajectory generation~\cite{morbidi2016minimum,kreciglowa2017energy}. Further, past mission planning approaches also limit to the trajectory~\cite{mei2004energy,mei2005case,mei2006deployment}, and to the class of robots~\cite{sadrpour2013mission,sadrpour2013experimental}. Yet, computations of such systems are only expected to increase in the near future. Unlike the past approaches, the algorithm presented here attempts to combine and generalize some of these technical breakthroughs and correlate the extensively studied energy planning to the growing computational demands.

The proposed algorithm alters the energy consumption dynamically by means of mission-specific parameters: the Quality of Service (QoS) of the onboard computations, and the trajectory-explicit equations (TEEs) of the path. Our goal is a mission extension by optimizing both QoS and TEEs as the UAV flies and its batteries drain. The algorithm optimizes QoS requiring the UAV to include robot operating system (ROS) nodes. It optimizes TEEs--an abstraction of the path to follow--and moves the UAV using a vector field that converges smoothly to the path. Physically, one can use a feature detection node and a set of ellipses, with the algorithm controlling the processing rate and the length of the semi-major and -minor axis. Data using a commercial fixed-wing UAV indicates a potential extension of up to 13 minutes over an hour by merely switching to the lowest QoS.

@@

We consider the problem of dynamic mission planning for a precision agriculture fixed-wing UAV. Precision agriculture is rising in demand for reducing waste, costs, and resources while increasing outputs and utilization~\cite{hajjaj2014review}, with mobile robots being increasingly used for e.g., harvesting~\cite{qingchun2012study,dong2011development, de2011design, aljanobi2010setup, li2008analysis, edan2000robotic}. In practice, complex monitoring strategies are often implemented utilizing UAVs and are usually required for preventing damage and ensuring better crop quality~\cite{puri2017agriculture}.

The UAV flies in ellipses shifted in time--a survey pattern optimized for the craft's dynamics--detects obstacles using a convolutional neural network (CNN) and informs ground mobile robots employed for future harvesting.

\subsection{Position and energy state}
\label{sec:model}

We use the state to estimate the UAV's position in space and the energy evolution in time. Starting with a position $\mathbf{p}\in\mathbb{R}^3$ in the 3D Euclidean space w.r.t. some inertial navigation frame $\mathcal{O}_W$, we build a guidance action--which allows the \emph{position evolution} along the 3-axis--to the path to follow using a vector field~\cite{de2017guidance}. The path is a set of generic continuous twice differentiable TEEs $\varphi_k:\mathbb{R}^3\rightarrow\mathbb{R}$. To this end, the TEE is satisfied $\varphi(\mathbf{p})\rightarrow 0$ for all the approaching points.

We build the \emph{energy evolution} $\mathbf{q}\in\mathbb{R}^j$ using Fourier analysis (the meaning of $j$ is clarified to the reader in Subsection~\ref{sec:energy-model}) and decompose such evolution in the energy due to the trajectory (depending on TEEs), and the computations (on QoS)--an approach adapted from our earlier work on computational energy analysis~\cite{seewald2019coarse, seewald2019component}, and energy estimation of a fixed-wing UAV~\cite{seewald2020mechanical}.

@@

We consider a non-holonomic 2D model of the UAV flying at an assigned altitude $h\in\mathbb{R}_{>0}$ (the requirement is eased in Section~\ref{sec:algo} to a set of altitudes $\mathbf{h}$)
\begin{equation}\label{eq:uav-kinem}\begin{cases}
  \dot{\mathbf{p}}(t)&=s\Psi(\psi(t))+\mathbf{d}(t)\\
  \dot{\psi}(t)&=u(\mathbf{p}(t))
\end{cases},
\end{equation}
where $\mathbf{p}\in\mathbb{R}^2$, $s\in\mathbb{R}$ is the airspeed (assumed constant), $\psi\in(-\pi,\pi]$ the attitude yaw angle and $\Psi(\psi)=\begin{bmatrix}\cos{\psi} & \sin{\psi}\end{bmatrix}^T$, $\mathbf{d}\in\mathbb{R}^2$ is the wind vector (assumed $\|\mathbf{d}\|<s$, i.e., the constant airspeed is greater than the norm of the wind), and $u\in\mathbb{R}$ the guidance action--the angular velocity $\dot{\psi}$ of the UAV.

@@

Let us define $\varPhi:=\varphi_k(\mathbf{p})-c_k$. The direction to follow can be expressed as the desired velocity vector
\begin{equation}\label{eq:pd}
  \dot{\mathbf{p}}_d(\mathbf{p}):=E\nabla\varPhi-k_e\varPhi\nabla\varPhi,\,\,\,E=\begin{bmatrix}
    0&1\\-1&0
  \end{bmatrix},
\end{equation}
where $\nabla\varPhi\in\mathbb{R}^2$ is defined as the gradient of $\varphi$ at the point $\mathbf{p}$ (i.e., its vector field), $E$ specifies the tracking direction, and $k_e\in\mathbb{R}_{\geq 0}$ the gain to adjusts the speed of convergence.

@@

The guidance action can be expressed
\begin{equation}\label{eq:uav-cont}
  u(\mathbf{p},\psi)=\frac{\|\dot{\mathbf{p}}\|}{s\cos{\gamma}}\left( \dot{\mathbf{\chi}}_d+k_d\hat{\dot{\mathbf{p}}}^TE\hat{\dot{\mathbf{p}}}_d \right),
\end{equation} 
where $\gamma=\cos^{-1}{\left( \hat{\dot{\mathbf{p}}}^T\Psi(\psi) \right)}$ is the sideslip angle, $k_d\in\mathbb{R}_{\geq 0}$ adjusts the speed of convergence of $\dot{\mathbf{p}}_d$, and $\dot{\chi}_d:=\dot{\chi}_d(\mathbf{p})$ is given in Equation~(\ref{eq:chid}).
